Parallel Sorting of Roughly-Sorted Sequences

### 2016-12-10 tex/pres.tex
typos

Comparison-based sorts are prone to divide-and-conquer and, therefore, opportunities for parallel speedup.
\end{frame}

@@

Threads, blocks, and grid all have identifiers
\newline\newline
Developer references these identfiers in code
\newline\newline
Using an understanding of how work is to be divided up among threads, these identifiers can inform a thread what work it needs to do

@@

% BEGIN PAR RADIUS
\begin{frame}
\frametitle{Parallel Radius Finding: Translating}
Back to parallel Roughsort: we know we can find the radius in parallel.  Merely need to convert the pseudocode to CUDA code.
\newline\newline
Straightforward for $LR$ list, slightly less so for $RL$, least straightforward for $DM$.
\newline\newline
Eventually settled on a $DM$ list determination based on the sequential, with array indicies fixed to thread ID.
\newline\newline
Added an efficient method to check for full array sortness as part of the $RL$ and $LR$ list components.
\end{frame}

@@

\begin{frame}
	\frametitle{Parallel Radius Finding: Scaling Up (2)}
	After fixing, $DM$ list was correct to an extent, but it was slow.
	\newline\newline
	Resolved this by realizing only need our "radius" to approximate the real $k$ value, in that we just need the next power of two greater
	\newline\newline
	Added \texttt{Thrust max_element} code to find the greatst value in the $DM$ list, thus yielding our radius
\end{frame}
% END PAR RADIUS

>>>>

Comparison-based sorts are prone to divide-and-conquer and rife with opportunities for parallel speedup.
\end{frame}

@@

Threads, blocks, and grid all have identifiers
\newline\newline
Developer references these identifiers in code
\newline\newline
Using an understanding of how work is to be divided up among threads, these identifiers can inform a thread what work it needs to do

@@

% BEGIN PAR RADIUS
\begin{frame}
\frametitle{Parallel Radius Finding: Translating}
Back to parallel Roughsort: we know we can find the radius in parallel.  Merely need to convert the pseudocode to CUDA code.
\newline\newline
Straightforward for $LR$ list, slightly less so for $RL$, least straightforward for $DM$.
\newline\newline
Eventually settled on a $DM$ list determination based on the sequential, with array indices fixed to thread ID.
\newline\newline
Added an efficient method to check for full array sortedness as part of the $RL$ and $LR$ list components.
\end{frame}

@@

\begin{frame}
	\frametitle{Parallel Radius Finding: Scaling Up (2)}
	After fixing, $DM$ list was correct to an extent, but it was slow.
	\newline\newline
	Resolved this by realizing only need our "radius" to approximate the real $k$ value, in that we just need the next power of two greater
	\newline\newline
	Added \texttt{Thrust max_element} code to find the greatest value in the $DM$ list, thus yielding our radius
\end{frame}
% END PAR RADIUS
